Global Value Chain Analysis of LMICs

### 2015-04-22 OECD-TiVa-LMIC-GVCs.Rmd
finish presentation

@@

 ```{r, echo=FALSE}
 # load the data
load("data/gvc_indicators.RData")
load("data/nrca_df.RData")
load("data/country_vars.RData")
load("data/w1995_2008.RData")
load("data/trca.RData")

@@

```{r, echo=FALSE}
w1995_2008 %>%
  group_by(year) %>%
  summarise( RDV = sum(RDV_INT) + sum(RDV_FIN) + sum(RDV_FIN2),
             PDC = sum(DDC_FIN) + sum(DDC_INT) + sum(ODC) + sum(MDC) ) %>%
  ggvis(~year, ~RDV, stroke="RDV") %>%
  layer_lines() %>%
  layer_lines(~year, ~PDC, stroke="PDC")
```

## GVC participation by *IC: I2E
Importing to Export (I2E)

@@

## GVC participation by *IC: E2R
Exporting to Re-export (E2R)

@@

## An application to new data: Confirming stylized facts

## An application to new data: Confirming stylized facts

## An application to new data: Confirming stylized facts

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(ctry) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik), avg_gdp = mean(avg_gdp) ) %>%
  ggvis(~avg_gdp, ~i2e ) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm")
```

## An application to new data: Confirming stylized facts

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(ctry) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik), nat_res_exp_sha_t_3 = mean(nat_res_exp_sha_t_3) ) %>%
  ggvis(~nat_res_exp_sha_t_3, ~i2e ) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm")
```

## An application to new data: Confirming stylized facts

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(ctry) %>%
  summarise(e2r = sum(dvar_ik) / sum(exports_ik), nat_res_exp_sha_t_3 = mean(nat_res_exp_sha_t_3) ) %>%
  ggvis(~nat_res_exp_sha_t_3, ~e2r ) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm")
```

## CEQ of China

@@

@@

>>>>

 ```{r, echo=FALSE, warnings=FALSE}
 # load the data
load("data/gvc_indicators.RData")
load("data/nrca_df.RData")
load("data/country_vars.RData")
load("data/w1995_2008.RData")
load("data/trca.RData")

@@

Rising value added in 3rd country exports.

@@

Increasing amounts of double counting indicate elongation of GVCs.

```{r, echo=FALSE}
w1995_2008 %>%
  group_by(year) %>%
  summarise( PDC = ( sum(DDC_FIN) + sum(DDC_INT) + sum(ODC) + sum(MDC) ) / sum(texp) ) %>%
  ggvis(~year, ~PDC) %>%
  layer_lines()
```

## I2E by industry

Distance to final demand predicts an industry's GVC participation.

```{r, echo=FALSE}
# i2e by industry
gvc_indicators %>%
  group_by(ind_name) %>%
  summarise(i2e = sum(fvax_ams_ik) * 100 / sum(exports_ik) ) %>%
  top_n(10) %>%
  ggvis(~factor(ind_name), ~i2e) %>%
  layer_bars() %>%
  add_axis("x", title = "industry name")
```

## E2R by industry

```{r, echo=FALSE}
# e2r by industry
gvc_indicators %>%
  group_by(ind_name) %>%
  filter(ind_name != "pvh" & ind_name != "edu" & ind_name != "egw" & ind_name != "con" & ind_name != "rea" & ind_name != "gov" & ind_name != "hth" & ind_name != "ptl") %>%
  summarise(e2r = sum(dvar_ik) * 100 / sum(exports_ik) ) %>%
  top_n(10) %>%
  ggvis(~factor(ind_name), ~e2r) %>%
  layer_bars() %>%
  add_axis("x", title = "industry name")
```

## I2E by country

country size and export composition determine GVC participation.

## E2R by country

## Natural Resources and E2R

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(ctry) %>%
  summarise(e2r = sum(dvar_ik) / sum(exports_ik), nat_res_exports = mean(nat_res_exp_sha_t_3) ) %>%
  ggvis(~nat_res_exports, ~e2r ) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm")
```

# GVC indicators for LMICs

## GVC participation by *IC: I2E

LMICs drive recent growth in GVC participation.

@@

## Sourcing I2E

```{r, echo=FALSE}
# i2e lo mi sourcing
gvc_indicators %>%
  group_by(year) %>%
  summarise(i2e_lic = sum(fvax_loinc_ams_ik) / sum(exports_ik),
            i2e_mic = sum(fvax_midinc_ams_ik) / sum(exports_ik),
            i2e_hic = sum(fvax_hiinc_ams_ik) / sum(exports_ik)) %>%
  ggvis(~year, ~i2e_lic, stroke = "i2e_lic" ) %>%
  layer_lines() %>%
  layer_lines(~year, ~i2e_mic, stroke="i2e_mic") %>%
  layer_lines(~year, ~i2e_hic, stroke="i2e_hic")
```

## GVC participation by *IC: E2R

@@

## Sourcing E2R

```{r, echo=FALSE}
# e2r lo mi sourcing
gvc_indicators %>%
  group_by(year) %>%
  summarise(e2r_lic = sum(dvar_loinc_ik) / sum(exports_ik),
            e2r_mic = sum(dvar_midinc_ik) / sum(exports_ik),
            e2r_hic = sum(dvar_hiinc_ik) / sum(exports_ik)) %>%
  ggvis(~year, ~e2r_lic, stroke = "e2r_lic" ) %>%
  layer_lines() %>%
  layer_lines(~year, ~e2r_mic, stroke="e2r_mic") %>%
  layer_lines(~year, ~e2r_hic, stroke="e2r_hic")
```

# New Indicators for GVC Analysis

## NRCA

Computer Equipment in China: Traditional overestimation

@@

## NRCA II

Motor and Transport Equipment: Traditional underestimation

```{r, echo=FALSE, } 
# TRCA vs NRCA for China, ELQ
gvc_indicators %>%
  filter(ctry == "tha") %>%
  filter(ind_name == "mtr") %>%
  group_by(year) %>%
  summarise( trca = sum(rca), nrca = sum(nrca) ) %>%
  ggvis(~year, ~trca, stroke = "trca") %>%
  layer_lines() %>%
  layer_lines(~year, ~nrca, stroke="nrca")
```

## I2E: Final Goods

Final-good assembly is relatively low-skilled.

```{r, echo=FALSE, warning=FALSE}
# FVA FIN china thailand india indonesia
w1995_2008 %>%
  filter(Exporting_Country == "chn" | Exporting_Country == "tha" | Exporting_Country == "ind" | Exporting_Country == "idn") %>%
  group_by(year, Exporting_Country) %>%
  summarise( I2E_FIN = ( sum(OVA_FIN) + sum(MVA_FIN) ) / sum(texp) ) %>%
  ggvis(~year, ~I2E_FIN, stroke = ~factor(Exporting_Country) ) %>%
  layer_lines()
```

## I2E: Intermediate Goods

Rising intermediate good exports indicate moving up the value chain.

```{r, echo=FALSE, warning=FALSE}
# FVA INT china thailand india indonesia
w1995_2008 %>%
  filter(Exporting_Country == "chn" | Exporting_Country == "tha" | Exporting_Country == "ind" | Exporting_Country == "idn") %>%
  group_by(year, Exporting_Country) %>%
  summarise( I2E_INT = ( sum(OVA_INT) + sum(MVA_INT) ) / sum(texp) ) %>%
  ggvis(~year, ~I2E_INT, stroke = ~factor(Exporting_Country) ) %>%
  layer_lines()
```

@@

  - new data
  - focus on LMICs

  - new indicators suited for non-traditional trade patterns
  - non-trivial linear algebra involved
  - simplified application of mew algorithms
  - many more indicators and tools available in the packages
    - decompr: decomposition
    - gvc: analysis
